A Transdiciplinary approach to developing a 3D spectral numerical coastal-flow model based on passive macroalgal rafting phenenomea to shed light on ambient and stochastic dispersal and connectivity of nearshore and offshore marine communities  around the coast of South Africa

### 2019-10-02 literature_review.Rmd
general updates and additions. added customised reference list. added in new tables which can be found under the taables subfolder

Dispersal is recognised as important driver of biodiveristy, composition and structure of ecological systems in the marine environment [@bernardes2018;@helmuth1994;@highsmith1985;macarthur2001;@jackson2010]. These processes are largely dependent on currents for dispersal of migrant populations which ultimately promote connectivity of marine ecosystems [@bernardes2018;@mackas1985;@mackas1985;@zakas2009]. This is particulary true for organisms which lack pelagic larvae, and are reliant on other modes of transport to reach new habitats through passive modes of dispersal from anthropogenic and natural sources. Anthropogenic sources include marine litter and structural debris while examples of organic sources include pumice and macroalgae in the form of kelp-rafts. Kelp-rafts have been identified as an important mode of passive dispersal of marine organisms, such as invertebrates [@helmuth1994; whichmann2012], epiphytes [@], grazers [@], invasive species [@] and macroalgae themselves [@] which either make landfall or are transported offshore where they eventually sink. A kelp-raft consists of an entanglement of macroalgae (one or multiple species) which have been dislodged from the benthic environment through hydrodynamic forces (mostly storms) and are positivley buoyant by means of gas-filled pneumatocysts and/or reproductive organs. Kelp-rafts are capable of travelling vast distances [@] and are considered important dispersal vectors in temperate latitudes, such as the Southern California Bight [@hobday2000] and the Northern Baltic Sea [@].

>>>>

Dispersal is recognised as important driver of biodiveristy, composition and structure of ecological systems in the marine environment [@bernardes2018;@helmuth1994;@highsmith1985;macarthur2001;@jackson2010]. These processes are largely dependent on currents for dispersal of migrant populations which ultimately promote connectivity of marine ecosystems [@bernardes2018;@mackas1985;@mackas1985;@zakas2009]. This is particulary true for organisms which lack pelagic larvae, and are reliant on other modes of transport to reach new habitats through passive modes of dispersal from anthropogenic and natural sources. Anthropogenic sources include marine litter and structural debris while examples of organic sources include pumice and macroalgae in the form of kelp-rafts. Kelp-rafts have been identified as an important mode of passive dispersal of marine organisms, such as invertebrates [@helmuth1994; whichmann2012], epiphytes [@], grazers [@nikula2010], invasive species [@lewis2005] and macroalgae themselves [@macaya2005] which either make landfall or are transported offshore where they eventually sink. A kelp-raft consists of an entanglement of macroalgae (one or multiple species) which have been dislodged from the benthic environment through hydrodynamic forces (mostly storms) and are positivley buoyant by means of gas-filled pneumatocysts and/or reproductive organs. Kelp-rafts are capable of travelling vast distances [@] and are considered important dispersal vectors in temperate latitudes, such as the Southern California Bight [@hobday2000] and the Northern Baltic Sea [@].
